Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-24 report/report.tex
Update todo
Rename implementation -> method

For the primary research question: the road overlap study, a program has taken a slice of the OSM dataset in the Stockholm area and assigned each road with standard withds according to swedish regulation.
It has then identified critical areas in the OSM dataset, where the paths are so wide that they collide with existing map features.
It has also identified how many of those areas can in theory be corrected by simple translation of the road vertices, without propagation of collision to other features.
Here, features are defined as the geometrical components that comprise the OSM map.
For the purpose of this report, features will refer mainly to roads and building footprints.
For the overlap study, see sections 3.1.2 for an implementation overview, 3.3 for a detailed walkthrough of the program implementation, and 4.1.1 for the results.

For the secondary research question: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM building dataset and the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy. See section 3.4.2 for an overview of the SLU dataset and how it is obtained.
The positional accuracy will be needed to assess where road overlap occurs and whether the collisions can easily be corrected.
For the positional accuracy study, see sections 3.1.1 for an implementation overview, 3.2 for a walkthrough of the program implementation, and 4.1.2 for the results.

@@

\chapter{Implementation}

@@

\section{Implementation overview}

Programmatic collection of statistics has been neccessary for both the primary and secondary research questions, and this section presents a broad overview of the technical implementation behind the map analysis and data collection processes for both the geodata precision study and the overlap study.

@@

% TODO: Even shorter abstract
% TODO: New structure: Background, problem/question, implementation/method, evaluation, results, implications
% TODO: Ensure in the abstract that it is visible that there are two research questions
% TODO: Restructure research subquestions according to Chris's suggestions (see meeting log)

% With internet
% TODO: Fix result table margins
% TODO: Spell check

>>>>

For the primary research question: the road overlap study, a program has taken a slice of the OSM dataset in the Stockholm area and assigned each road with standard withds according to swedish regulation.
It has then identified critical areas in the OSM dataset, where the paths are so wide that they collide with existing map features.
It has also identified how many of those areas can in theory be corrected by simple translation of the road vertices, without propagation of collision to other features.
Here, features are defined as the geometrical components that comprise the OSM map.
For the purpose of this report, features will refer mainly to roads and building footprints.
For the overlap study, see sections 3.1.2 for a method overview, 3.3 for a detailed walkthrough of the method, and 4.1.1 for the results.

For the secondary research question: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM building dataset and the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy. See section 3.4.2 for an overview of the SLU dataset and how it is obtained.
The positional accuracy will be needed to assess where road overlap occurs and whether the collisions can easily be corrected.
For the positional accuracy study, see sections 3.1.1 for a method overview, 3.2 for a walkthrough of the method, and 4.1.2 for the results.

@@

\chapter{Method}

@@

\section{Method overview}

Programmatic collection of statistics has been neccessary for both the primary and secondary research questions, and this section presents a broad overview of the technical details behind the map analysis and data collection processes for both the geodata precision study and the overlap study.

@@

% TODO: New structure: Background, problem/question, implementation/method, evaluation, results, implications

% With internet
% TODO: Restructure research subquestions according to Chris's suggestions (see meeting log)
% TODO: Fix result table margins
% TODO: Spell check
